---
title: "Introduction to CohortSymmetry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a01_Introduction_to_CohortSymmetry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  eval = Sys.getenv("$RUNNER_OS") != "macOS"
)
```

CohortSymmetry provides tools to perform a Sequence Symmetry Analysis (SSA). The main functions you will interact with are:

1.  `generateSequenceCohortSet()`: this function will create a cohort with individuals present in both, the index and the marker cohort.

2.  `summariseSequenceRatio()`: this function will calculate the sequence ratio.

3.  `tableSequenceRatios()`, `plotSequenceRatio()` and `plotTemporalSymmetry()`: these functions will help us to visualise the results.

Below, you will find an example analysis that offers a comprehensive overview of the package's functionalities. More context and further examples for each of these functions are provided in later vignettes.

First, let’s load the relevant libraries.

```{r message= FALSE, warning=FALSE}
library(CDMConnector)
library(dplyr)
library(DBI)
library(omock)
library(CohortSymmetry)
library(duckdb)
```

The CohortSymmetry package works with data mapped to the OMOP CDM. Hence, the initial step involves connecting to a database. As an example, we will be using Omock package to generate a mock database with two mock cohorts: the **index_cohort** and the **marker_cohort**.

```{r message= FALSE, warning=FALSE}
cdm <- emptyCdmReference(cdmName = "mock") |>
  mockPerson(nPerson = 100) |>
  mockObservationPeriod() |>
  mockCohort(
    tableName = "index_cohort",
    numberCohorts = 1,
    cohortName = c("index_cohort"),
    seed = 1,
  ) |>
  mockCohort(
    tableName = "marker_cohort",
    numberCohorts = 1,
    cohortName = c("marker_cohort"), 
    seed = 2
  )

con <- dbConnect(duckdb::duckdb())
cdm <- copyCdmTo(con = con, cdm = cdm, schema = "main")

cdm
```

Once we have established a connection to the database, we can use the `generateSequenceCohortSet()` function to find the intersection of the two cohorts. This function will provide us with the individuals who appear in both cohorts.

```{r message= FALSE, warning=FALSE}
cdm <- generateSequenceCohortSet(
  cdm = cdm,
  indexTable = "index_cohort",
  markerTable = "marker_cohort",
  name = "intersect"
)
```

See below that the generated cohort follows the format of an OMOP CDM cohort with the addition of two extra columns: *index_date* and *marker_date*. These columns correspond to the *cohort_start_date* in the **index_cohort** and the **marker_cohort**, respectively.

```{r message= FALSE, warning=FALSE}
cdm$intersect
```

Observe that, automatically, in the settings of the generated cohort we will be able to identify which cohort corresponds to the indexTable and which one to the markerTable, as cohort_name has the following form:

<center>
*index*\_{indexTable}_*marker*\_{markerTable}
</center>
```{r message= FALSE, warning=FALSE}
settings(cdm$intersect)
```

Once we have the **intersect** cohort, you are able to explore the temporal trend by using `plotTemporalSymmetry()`:
```{r message= FALSE, warning=FALSE}
plotTemporalSymmetry(cdm = cdm,
                     joinedTable = "intersect")
```

Next, we will use the `generateSequenceCohortSet()` function to get the crude sequence ratios, adjusted sequence ratios, and the corresponding confidence intervals. 
```{r message= FALSE, warning=FALSE}
result <- summariseSequenceRatio(cdm = cdm,
                                 sequenceTable = "intersect")

result
```
Finally, we can visualise the results using `tableSequenceRatios()`:
```{r message= FALSE, warning=FALSE}
tableSequenceRatios(result)
```
Or create a plot with the adjusted sequence ratios:

```{r message= FALSE, warning=FALSE}
plotSequenceRatio(cdm = cdm,
                  joinedTable = "intersect",
                  sequenceRatio = result,
                  onlyaSR = T,
                  colours = "black")
```
