---
title: "Step 2. Obtain the sequence ratios"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a03_Summarise_sequence_ratio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  eval = Sys.getenv("$RUNNER_OS") != "macOS"
)
```

```{r, include = FALSE}
if (Sys.getenv("EUNOMIA_DATA_FOLDER") == "") Sys.setenv("EUNOMIA_DATA_FOLDER" = tempdir())
if (!dir.exists(Sys.getenv("EUNOMIA_DATA_FOLDER"))) dir.create(Sys.getenv("EUNOMIA_DATA_FOLDER"))
if (!CDMConnector::eunomia_is_available()) CDMConnector::downloadEunomiaData()
```

# Introduction
In this vignette we will explore the functionality and arguments of `summariseSequenceRatio()` function, which is used to generate the sequence ratios of the SSA. As this function uses the output of `generateSequenceCohortSet()` function (explained in detail in the vignette: **Step 1. Generate a sequence cohort**), we will pick up the explanation from where we left off in the previous vignette. 

Hence, let's start by generating the sequence cohort table:

```{r message= FALSE, warning=FALSE}
# Load libraries
library(CDMConnector)
library(dplyr)
library(DBI)
library(CohortSymmetry)
library(duckdb)
library(DrugUtilisation)

# Connect to the database
db <- DBI::dbConnect(duckdb::duckdb(), 
                     dbdir = CDMConnector::eunomia_dir())
cdm <- cdm_from_con(
  con = db,
  cdm_schema = "main",
  write_schema = "main"
)

# Generate cohorts
cdm <- DrugUtilisation::generateIngredientCohortSet(
  cdm = cdm,
  name = "aspirin",
  ingredient = "aspirin")

cdm <- DrugUtilisation::generateIngredientCohortSet(
  cdm = cdm,
  name = "acetaminophen",
  ingredient = "acetaminophen")

# Generate a sequence cohort
cdm <- generateSequenceCohortSet(
  cdm = cdm,
  indexTable = "aspirin",
  markerTable = "acetaminophen",
  name = "intersect",
  combinationWindow = c(0,Inf))
```


# Obtain the sequence ratios
One can obtain the crude and adjusted sequence ratios (with its corresponding confidence intervals) using `summariseSequenceRatio()` function:
```{r message = FALSE, warning = FALSE}
summariseSequenceRatio(
  cohort = cdm$intersect
) |>
  glimpse()
```
The obtained output has a summarised result format. In the later vignette (**Step 3. Visualise results**) we will explore how to visualise the results in a more understandable way. 

## Modify the confidence interval
By default, the `summariseSequenceRatio()` function will use 95% confidence interval. If another confidence interval is desired, one can use the `confidenceInterval` argument:
```{r message = FALSE, warning = FALSE}
summariseSequenceRatio(
  cohort = cdm$intersect,
  confidenceInterval = 99) |>
  glimpse()
```

## Modify the moving window
We define the moving window as the specified number of days for observation time window. This is mainly used to calculate the null sequence ratio (please, refer to Reference<sup>1</sup> for more details on this parameter). By default, the argument is defined as `movingAverageRestriction = 548` <sup>2</sup>, but can be modified:
```{r message = FALSE, warning = FALSE}
summariseSequenceRatio(
  cohort = cdm$intersect,
  movingAverageRestriction = 600) |>
  glimpse()
```

# References
1. Lai EC, Pratt N, Hsieh CY, Lin SJ, Pottegård A, Roughead EE, Kao Yang YH, Hallas J. Sequence symmetry analysis in pharmacovigilance and pharmacoepidemiologic studies. Eur J Epidemiol. 2017 Jul;32(7):567-582. doi: 10.1007/s10654-017-0281-8. Epub 2017 Jul 11. PMID: 28698923.
2. Tsiropoulos I, Andersen M, Hallas J. Adverse events with use of antiepileptic drugs: a prescription and event symmetry analysis. Pharmacoepidemiol Drug Saf. 2009 Jun;18(6):483-91. doi: 10.1002/pds.1736. PMID: 19326363.
