---
title: "Step 3. Visualise the sequence ratios"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a04_Visualise_sequence_ratios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  eval = Sys.getenv("$RUNNER_OS") != "macOS"
)
```

```{r, include = FALSE}
if (Sys.getenv("EUNOMIA_DATA_FOLDER") == "") Sys.setenv("EUNOMIA_DATA_FOLDER" = tempdir())
if (!dir.exists(Sys.getenv("EUNOMIA_DATA_FOLDER"))) dir.create(Sys.getenv("EUNOMIA_DATA_FOLDER"))
if (!CDMConnector::eunomia_is_available()) CDMConnector::downloadEunomiaData()
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction
In this vignette we will explore the functionality and arguments of a set of functions that will help us to understand and visualise the results using a user-friendly set-up. In particular, we will delve into the following functions:

- `plotTemporalSymmetry()`: to plot the temporal trend of the index and marker cohorts.
- `tableSequenceRatios()`: to generate a gt table summarising the results.
- `plotSequenceRatio()`: to plot the sequence ratios.

This function builds-up on previous functions, such as `generateSequenceCohortSet()` and `summariseSequenceRatio()` function (explained in detail in previous vignettes: **Step 1. Generate a sequence cohort**, and **Step 2. Summarise sequence ratio**). Hence, we will pick up the explanation from where we left off in the previous vignette. 

```{r message= FALSE, warning=FALSE}
# Load libraries
library(CDMConnector)
library(dplyr)
library(DBI)
library(CohortSymmetry)
library(duckdb)
library(DrugUtilisation)

# Connect to the database
db <- DBI::dbConnect(duckdb::duckdb(), 
                     dbdir = CDMConnector::eunomia_dir())
cdm <- cdm_from_con(
  con = db,
  cdm_schema = "main",
  write_schema = "main"
)

# Generate cohorts
cdm <- DrugUtilisation::generateIngredientCohortSet(
  cdm = cdm,
  name = "aspirin",
  ingredient = "aspirin")

cdm <- DrugUtilisation::generateIngredientCohortSet(
  cdm = cdm,
  name = "acetaminophen",
  ingredient = "acetaminophen")

# Generate a sequence cohort
cdm <- generateSequenceCohortSet(
  cdm = cdm,
  indexTable = "aspirin",
  markerTable = "acetaminophen",
  name = "intersect",
  combinationWindow = c(0,Inf))

# Calculate the sequence ratio
result <- summariseSequenceRatio(
  cohort = cdm$intersect
)
```

# Plot the temporal trend of the index and marker cohorts
```{r message= FALSE, warning=FALSE}

```

